Modeling the Java Card API in B

### 2012-04-02 trunk/papers/B2012-work/javacardAPIpaper.tex
mudancas david

AMM: TRECHOS EXTRAIDOS E JA UM POUCO ALTERADOS DO ABZ 2010. DEPENDENDO
DO QUE VAMOS MOSTRAR NA ESPECIFICAÇAO PODEMOS DEIXAR MAIS OU MENOS
DETALHES AQUI. NO FINAL, PRECISAMOS VERIFICAR QUE NAO COPIAMOS DEMAIS
O QUE ESTAVA LA.

A smart card application is distributed between on-card and off-card
components.  The server application on the card side (called applet)
provides the application services. The off-card client (called host
application) resides in a computer or electronic terminal.

The information exchange between the host and card applications is
made through a a half-duplexed low level protocol, named
\emph{Application Protocol Data Unit} (APDU).  The ISO 7816-4 standard
specifies two kinds of APDU's, which are the command and the response
APDU (Figure~\ref{fig:APDUs}). Both specify data packets. A command APDU
is sent by the host, requiring some applet service and a response APDU is
sent by the applet, responding to the host request with the result of the
service processing.

\begin{figure}[!ht]
\centering
%\includegraphics[scale=0.3]{figs/comandoAPDU.jpg}
%\includegraphics[scale=0.3]{figs/respostaAPDU.jpg}
\caption{Command and response APDUs. Source:~\cite{ortiz1intro:2003}}
\label{fig:APDUs}
\end{figure}

@@

\begin{figure}[h]
\centering
%\includegraphics[width=0.35\textwidth]{figs/jcplatform.png}
\caption{Java Card platform components. Adapted from:~\cite{ortiz1intro:2003}}
\label{fig:jcre}
\end{figure}

@@

\lstset{language=B, caption={B machine Buscard},label=lis:object}
\begin{lstlisting}
MACHINE Object
SEES  ObjectSet
OPERATIONS
 	result <-- equals(obj) =
	PRE obj : OBJECT   /* declared in the ObjectSet machine */
	THEN
		result :: {TRUE, FALSE}
	END
END

@@

The models are used in the different phases of the 
BSmart method development. Initially, the application 
abstract specification uses the models of basic Java types, 
since Java Card specific aspects are ideally related only
in subsequent refinements.

@@

In the B implementation, the whole set of the API can be related. Usually, besides
ISOException (or other exception model), in a typical Java Card development 
are imported \emph{Apdu} and \emph{Util}  modules. The fist defines operations
to start the process of receiving (from host) and sending (to host) information 
through the \emph{apdu buffer}. The preconditions of these sending/receiving 
operations aid the verification process, since the specifier must to observe 
the correct order in operation calling. The \emph{Util} component contains useful 
operations to effectively get and put data in the buffer. When translating to 
\emph{Java Card} the operation calling are translated to the corresponding 
\emph{Java Card} method.

>>>>

A smart card application is distributed between on-card and off-card
components.  The server application on the card side (called applet)
provides the application services. The off-card client (called host
application) resides in a computer or electronic terminal. The information 
exchange between the host and card applications is
made through a a half-duplexed low level protocol, named
\emph{Application Protocol Data Unit} (APDU).

@@

The Java Card API provides the means to deal with the APDU protocol,

@@

\lstset{language=B, caption={Basic API Definitions},label=lis:object}
\begin{lstlisting}
MACHINE Object
SEES  ObjectSet
OPERATIONS
 	result <-- equals(obj) =
	PRE obj : OBJECT   /* declared in the ObjectSet machine */
	THEN
		result :: {TRUE, FALSE}
	END
END

@@

The models of the Java Card API are used in the different phases of the 
BSmart method development. Initially, the application 
abstract specification uses the models of basic Java types, 
since Java Card specific aspects are ideally related only
in subsequent refinements.

@@

In the B implementation, the whole API can be referenced. Usually,
besides ISOException (or another exception model), a typical Java Card
development imports the \emph{Apdu} and \emph{Util} modules. The first
defines operations to start the process of receiving (from host) and
sending (to host) information through the \emph{apdu buffer}. The
preconditions of these sending/receiving operations aid the
verification process, since the specifier must observe the correct
order of operation calls. The \emph{Util} component contains useful
operations to effectively get and put data in the buffer. When
translating to \emph{Java Card} the operation calls are translated
to the corresponding \emph{Java Card} method.
